Ladies' figure skating in the 2002 Winter Olympics

### 2024-03-05 inst/skating.Rmd
typo

Looking at the above, we see that Hughes has five judges who gave her
"1"s, while Slutskaya has only 4, which is why she was considered to
be the top.  It seems that Hughes's two "4"s (compared with
Slutskaya's one) have cost her more likelihood-based strength than her
extra "1" gave her; note also that the two judges who placed Highes
fourth (viz `J2` and `J4`) placed Slutskaya first.  Also:

>>>>

Looking at the above, we see that Hughes has five judges who gave her
"1"s, while Slutskaya has only 4, which is why she was considered to
be the top.  It seems that Hughes's two "4"s (compared with
Slutskaya's one) have cost her more likelihood-based strength than her
extra "1" gave her; note also that the two judges who placed Hughes
fourth (viz `J2` and `J4`) placed Slutskaya first.  Also:
